Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-14 paper/paper.qmd
Finished sampling approach

The sampling approach taken by The Washington Post [@datahomicides] is non-probabilistic sampling and more specifically, purposive sampling [@citePurposiveSampling]. @datahomicides were interested in homicide cases from 2007 to 2017 from the 50 largest US cities and purposive sampling would allow them to have a sample that fit their sampling frame. However, @citePurposiveSampling noted that

- what is the population, frame, and sample;
- how is the sample recruited;
- how is non-response handled; - They marked it as "Unknown" or left the field blank.

- what sampling approach is taken, and what are some of the trade-offs of this;

>>>>

The sampling approach taken by The Washington Post [@datahomicides] is non-probabilistic sampling and more specifically, purposive sampling [@citePurposiveSampling]. @datahomicides were interested in homicide cases from 2007 to 2017 from the 50 largest US cities and purposive sampling would allow them to have a sample that fit their sampling frame. However, @citePurposiveSampling noted that a tradeoff of purposive sampling is that it is prone to research bias since researchers have to make judgement such as the size of the sample and why. For example, why is it that The Washington Post decided to choose the 50 largest US cities instead of the 20 largest US cities?
